Post-Disturbance Tree Community Trajectories in a Neotropical Forest

### 2018-06-24 WholePlotTrajectories.tex
Update WholePlotTrajectories.tex

The taxonomic and functional trajectories validated the IDH as
determinant of communities functional structure and of the dominant
species pool, while contrastingly the pool of rare species relied upon
more stochastic processes.

The disturbance intensity poorly predicted the taxonomic richness, as
already observed in the Paracou station \citep{Baraloto2012a} and in
Bornean tropical forests \citep{Cannon1998}, was only weakly correlated
with the increase in taxonomic evenness (\emph{i.e.} Simpson diversity).

Contrastingly, the disturbance intensity consistently predicted the
increase in functional diversity after disturbance along the 30 years.
The functional diversity increase paralleled the significant specific
turnover and functional shifts towards resource-acquisitive strategies
(sharp increase in the SLA, leaf thickness and bark thickness and
decrease in wood density, leaf toughness and maximum height)
\citep{Westoby1998, Wright2004, Reich2014}. As the old-growth,
pre-disturbance survivor trees proved mirroring the initial communities
\citep{Herault2018} the functional trajectories and taxonomic turnover
rather relied upon the pool of newly recruited trees driven by the
enhanced growth and survival of previously infrequent species and
functional types. Disturbance entailed a reorganization, benefiting to
pioneers and light demanding species, of the typical high dominance
structure of hyperdiverse mature forests. The changes in abiotic
environment and competitive pressure favored pioneers which outcompeted
other species in non limiting light resources but were excluded in
mature forests by long-lived, more resistant and shade tolerant species.
Disturbance trajectories therefore relied upon the environmental niches
made available and filled by species from a restricted functional range
that became dominant and structured the functional characteristics of
the community \citep{Grime1998}. The intermediate disturbance hypothesis
was suitabe to predict communities functional diversity and pool of
dominant species \citep{Molino2001}, but it poorly represented the whole
taxonomic structure that was hampered by the slow recovery of rare
species \citep{Hubbell2001, Chave2004}.

>>>>

Disturbance intensity poorly predicted the taxonomic richness regardless of the period studied, as
already observed in the Guiana Shield \citep{Baraloto2012a} and in
Bornean tropical forests \citep{Cannon1998}. Contrastingly, the disturbance intensity consistently predicted the
increase in functional diversity after disturbance along the 30 years.
The functional diversity increase paralleled the significant functional shifts towards resource-acquisitive strategies
(sharp increase in the SLA, leaf thickness and bark thickness and
decrease in wood density, leaf toughness and maximum height)
\citep{Westoby1998, Wright2004, Reich2014}. As the old-growth,
pre-disturbance survivor trees proved mirroring the initial communities
\citep{Herault2018} the functional trajectories and taxonomic turnover
rather relied upon the pool of newly recruited trees driven by the
enhanced growth and survival of previously infrequent species and
functional types. Disturbance entailed a reorganization, benefiting to
pioneers and light demanding species, of the typical high dominance
structure of hyperdiverse mature forests. The changes in abiotic
environment and competitive pressure favored pioneers which outcompeted
other species in non limiting light resources but were excluded in
mature forests by long-lived, more resistant and shade tolerant species.

* Not clear from here*
Disturbance trajectories therefore relied upon the environmental niches
made available and filled by species from a restricted functional range
that became dominant and structured the functional characteristics of
the community \citep{Grime1998}. The intermediate disturbance hypothesis
was suitabe to predict communities functional diversity and pool of
dominant species \citep{Molino2001}, but it poorly represented the whole
taxonomic structure that was hampered by the slow recovery of rare
species \citep{Hubbell2001, Chave2004}.
